{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-03 bmvc_review.tex
Comment Answered
Another editing.

\textbf{Performance on UAV123$\_$10fps Dataset.} It maybe a slight
digression from the main idea -- the idea of deploying multiple KCFs
to make a very fast and effective, single target tracking
available. We found that, with a slight modification, the proposed
method can effectively handle tracking of object in fast motion and in
large camera motion.

{\it Burak: What modification we made to change {\it E}nKCF to {\it E}nKCF2?}

In particular, the UAV123 data has another version where the original
dataset was temporally down-sampled at $10$ fps and makes the
challenging original dataset, because of objects in fast motion and
large ego-motion, more challenging. This is because the magnitude of
those motions is even bigger. Figure \ref{fig:UAV123_10fpsDATASET}
compares the performance of the modified version of {\it E}nKCF and
other tracking methods. Our tracker outperforms other high-speed
correlation filter based trackers including KCF, DSST by about
$15\%$-$20\%$ and showed a precision rate similar to that of SAMF. On
the other hand, it does decent job in scale estimation. It ranks as
second in AUC while running about $150$ faster than the MUSTER
tracker.
\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Precision_UAV123_10fps.pdf}}
\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_UAV123_10fps.pdf}}\\
\end{tabular}
\caption{Evaluation and comparison of the proposed {\it E}nKCF2 tracker on the UAV123$\_$ dataset in terms of the precision and success rates. This dataset consists of temporally downsampled $123$ video sequences captured from a micro UAV.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}

>>>>

\textbf{Performance on UAV123$\_$10fps Dataset.} It maybe a slight
digression from the main idea -- the idea of deploying multiple KCFs
to make a very fast and effective, single target tracking
available. We found that, with a slight modification, the proposed
method can effectively handle tracking of object in fast motion and in
large camera motion. Specifically we modified {\it E}nKCF by running
$R_{t}^{L}$ every frame and remove the particle filter instead. We
tested this modified {\it E}nKCF with another vision of the UAV123 that
the original dataset was temporally down-sampled at $10$ fps and makes
the challenging original dataset, because of objects in fast motion
and large ego-motion, more challenging. This is because the magnitude
of those motions is even bigger. Figure \ref{fig:UAV123_10fpsDATASET}
compares the performance of the modified version of {\it E}nKCF and
other tracking methods. Our tracker outperforms other high-speed
correlation filter based trackers including KCF, DSST by about
$15\%$-$20\%$ and showed a precision rate similar to that of SAMF. On
the other hand, it does decent job in scale estimation. It ranks as
second in AUC while running about $150$ faster than the MUSTER
tracker.
\begin{figure}[!h]
\centering
\begin{tabular}{cc}
\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Precision_UAV123_10fps.pdf}}
\bmvaHangBox{\includegraphics[width=4.0cm]{./figures/Success_UAV123_10fps.pdf}}\\
\end{tabular}
\caption{Evaluation and comparison of the proposed {\it E}nKCF2 tracker on the UAV123$\_$ dataset in terms of the precision and success rates. This dataset consists of temporally downsampled $123$ video sequences captured from a micro UAV.}
\label{fig:UAV123_10fpsDATASET}
\end{figure}
